Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-24 robdml.tex
tex

\input{tab-hmeff.tex}
% 1. possible combinations

In literature, various triplet sampling strategies exist, such as random,
semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance},
and the hardest negative sampling (\ie, the negative sample with the largest
loss value).
%
Although any of them can be selected for source or destination hardness for HM,
not all the possible combinations are expected to be effective or efficient.
%
In order to figure out an empirically good combination of source and
destination hardness, we adversarially train RN18 models on the CUB dataset
with every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.
%
Note, these methods are empirically sorted by their expectation of hardness
$E[H]$, in the ascending order: random, semihard, softhard, distance, and
hardest, as shown in \cref{tab:hsort}.

>>>>

\input{tab-hmeff.tex}

% 1. possible combinations

Although any of the existing triplet sampling strategies, such as Random,
Semihard~\cite{facenet}, Softhard~\cite{revisiting},
Distance-weighted~\cite{distance}, and the within-batch Hardest negative
sampling method, can be selected for source and destination hardness,
not all combinations are effective and efficient.
%
In this subsection, we find a proper combination empirically.

% 2. sort sampling strategies

As HM is expected to increase the hardness of the source triplet, we first sort
the triplet sampling methods according to their approximated mean hardness of
$1000$ mini-batches from CUB dataset with an imagenet-initialized RN18 model,
as shown in~\cref{tab:hsort}.

In order to figure out an empirically good combination of source and
destination hardness, we adversarially train RN18 models on the CUB dataset
with every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.
%
Note, these methods are empirically sorted by their expectation of hardness
$E[H]$, in the ascending order: random, semihard, softhard, distance, and
hardest, as shown in \cref{tab:hsort}.
